\bf Cognitive control and semantic thought variability\\across sleep and wakefulness

### 2024-12-15 manuscript/manuscript.tex
remove figure links
add ORCIDs

\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage{authblk}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{csquotes}
\usepackage{newtxtext,newtxmath} % access Times New Roman
\usepackage{microtype} % prettifies typesetting and prevents some overfulls
\usepackage{parskip} % sets space between paragraphs
\usepackage{graphicx} % figures
\usepackage{booktabs} % tables
\usepackage[font=small,labelfont=bf,labelsep=period,singlelinecheck=false]{caption} % captions
\usepackage[backend=biber,style=nature,date=year,hyperref=false]{biblatex} % references
\usepackage[final,hyperfootnotes=false,hidelinks]{hyperref} % hyperlinks
\addbibresource{references.bib}

@@

\title{\bf Cognitive control and semantic thought variability\\across sleep and wakefulness}
\author[1]{Remington Mallett\thanks{correspondence: \href{mailto:mallett.remy@gmail.com}{\texttt{mallett.remy@gmail.com}}}}
\author[1]{Yasmeen Nahas}
\author[2]{Kalina Christoff}
\author[1]{Ken A. Paller}
\author[3]{Caitlin Mills}
\affil[1]{Department of Psychology, Northwestern University, Evanston, IL, USA}
\affil[2]{Department of Psychology, University of British Columbia, Vancouver, BC, CA}
\affil[3]{Department of Educational Psychology, University of Minnesota, Minneapolis, MN, USA}
\date{}

>>>>

\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\usepackage[affil-it]{authblk}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{csquotes}
\usepackage{newtxtext,newtxmath} % access Times New Roman
\usepackage{microtype} % prettifies typesetting and prevents some overfulls
\usepackage{parskip} % sets space between paragraphs
\usepackage{graphicx} % figures
\usepackage{booktabs} % tables
\usepackage[font=small,labelfont=bf,labelsep=period,singlelinecheck=false]{caption} % captions
\usepackage[backend=biber,style=nature,date=year,hyperref=false]{biblatex} % references
\usepackage[final,hyperfootnotes=false,hyperfigures=false,hidelinks]{hyperref} % hyperlinks
\usepackage{orcidlink} % ORCID iDs
\addbibresource{references.bib}

@@

\renewcommand\Authands{, \& }

\title{\bf Cognitive control and semantic thought variability\\across sleep and wakefulness}
\author[1]{Remington~Mallett~\orcidlink{0000-0001-6183-3098}\thanks{correspondence:~\href{mailto:mallett.remy@gmail.com}{\texttt{mallett.remy@gmail.com}}}}
\author[1]{Yasmeen~Nahas}
\author[2]{Kalina~Christoff~\orcidlink{0000-0003-2841-8647}}
\author[1]{Ken~A.~Paller~\orcidlink{0000-0003-4415-4143}}
\author[3]{Caitlin~Mills~\orcidlink{0000-0003-4498-0496}}
\affil[1]{Department~of~Psychology, Northwestern~University, Evanston,~IL,~USA}
\affil[2]{Department~of~Psychology, University~of~British~Columbia, Vancouver,~BC,~CAN}
\affil[3]{Department~of~Educational~Psychology, University~of~Minnesota, Minneapolis,~MN,~USA}
\date{}
